fdcoexist

### 2018-09-04 paper_simulations.Rmd
:memo: better values for competition parameter

# Competition + Dispersion coefficients
B = 1/500 # Scalar for intraspecific competition
A =  B/n_species	# Alpha scalar
d = 0.05 # Dispersal percentage

@@

# Graphical parameters ---------------------------------------------------------
theme_set(theme_bw(12))

@@

@@

# R2 plot
plot_r2_cwm_env = ggplot(mod_df %>%
                             filter(!grepl("growth", cwm_name)),
                         aes(scenario, r.squared)) +
    geom_point(aes(fill = fct_rev(cor_level)),
               size = 4, position = position_dodge(width = 0.7),
               shape = 21) +
    facet_grid(rows = vars(compet_status), cols = vars(env_width, cwm_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength"))) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(subtitle = "R2 of trait2 CWM ~ environment",
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

@@

```{r plot_trait_var_env}
all_trait_var = all_df %>%
    filter(N > 0) %>%
    group_by(env_width, compet_status, cor_level, scenario, patch) %>%
    summarise_at(vars(matches("trait[123]$")), funs(var = var(.))) %>%
    ungroup() %>%
    mutate(patch_optim = as.numeric(gsub("patches", "", patch))) %>%
    gather("trait_name", "trait_value", contains("trait"))

plot_trait_var_env_constant = ggplot(all_trait_var %>%
                                         filter(env_width == "constant"),
                                     aes(patch_optim, trait_value,
                                         color = trait_name,
                                         linetype = compet_status)) +
    geom_line() +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(name = "Trait",
                         labels = c(trait1_var = "Trait 1",
                                    trait2_var = "Trait 2",
                                    trait3_var = "Trait 3")) +
    scale_linetype_discrete(name = NULL,
                            labels = c(compet    = "Competition",
                                       no_compet = "Only intra comp.")) +
    labs(x = "Environment",
         y = "Trait Variance",
         subtitle = "Constant Environment") +
    theme(legend.position = "top")

@@

plot_trait_var_env_varying

```{r link_r2_cwm_trait_var}

mod_df$contrib2 <- as.numeric(gsub(".*R|A.*", "",
                                   mod_df$scenario))
mod_df$contrib1 <- 100 - mod_df$contrib2

all_trait_var$contrib2 <- as.numeric(gsub(".*R|A.*", "",
                                          all_trait_var$scenario))
all_trait_var$contrib1 <- 100 - all_trait_var$contrib2

# Plot
plot_grid(
    ggplot(mod_df[which(mod_df$env_width == "constant" &
                            mod_df$compet_status == "compet" &
                            mod_df$cwm_name == "trait2_cwm"), ],
           aes(as.factor(contrib2), adj.r.squared)) +
        geom_boxplot(aes(fill = cor_level)) +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(x = "Contribution of trait2 to growth (in %)",
             y = "R² of the relationship between\nCWM and environment"),
    ggplot(all_trait_var[which(all_trait_var$compet_status == "compet" &
                                   all_trait_var$env_width == "constant" &
                                   all_trait_var$trait_name == "trait2_var"), ],
           aes(as.factor(contrib2), trait_value)) +
        geom_boxplot(aes(fill = cor_level)) +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(x = "Contribution of trait2 to growth (in %)",
             y = "Variance of trait2 within the patch"),
    nrow = 2)

ggplot(all_trait_var, aes(scenario, trait_value, fill = fct_rev(cor_level))) +
    geom_boxplot() +
    facet_grid(rows = vars(env_width, compet_status),
               cols = vars(trait_name),
               labeller =
                   labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength")),
               scales = "free_y") +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(y = "Variance of trait across all patches")

@@

```{r cwv_envt}

var_df %>%
    select(-contains("cwm")) %>%
    filter(compet_status == "no_compet") %>%
    gather("trait_name", "trait_value", contains("trait")) %>%
    group_by(compet_status, cor_level, scenario, patch, trait_name) %>%
    summarise(trait_cwv = Weighted.Desc.Stat::w.var(trait_value, mu = N)) %>%
    mutate(patch_optim = gsub("patches", "", patch) %>%
               as.numeric()) %>%
    ggplot(aes(patch_optim, trait_cwv, color = trait_name)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(labels = c(trait1_cwm = "Trait 1",
                                    trait2_cwm = "Trait 2",
                                    trait3_cwm = "Trait 3")) +
    labs(x = "Environment",
         y = "Community-Weighted Variance (CWV)",
         color = NULL,
         subtitle = paste0("Varying environment; ",
                           d * 100, "% dispersal;",
                           " Only intra comp.")) +
    theme(legend.position = "top")

>>>>

# Competition + Dispersion coefficients
B = 2e-4 # Scalar for intraspecific competition
A = B	# Alpha scalar
d = 0.05 # Dispersal percentage

@@

# Graphical parameters ---------------------------------------------------------
theme_set(theme_bw(12) +
              theme(axis.text.x = element_text(angle = 45),
                    legend.text = element_text(angle = 45)))

@@

label_compet_env = labeller(compet_status = c(compet = "Competition",
                                              no_compet = "Only intra comp."),
                            env_width     = c(constant = "Constant\nEnv. Filter Strength",
                                              varying  = "Varying\nEnv. Filter Strength"))

@@

# R2 plot
plot_r2_cwm_env = ggplot(mod_df %>%
                             filter(!grepl("growth", cwm_name)),
                         aes(scenario, r.squared)) +
    geom_point(aes(fill = fct_rev(cor_level)),
               size = 4, position = position_dodge(width = 0.7),
               shape = 21) +
    facet_grid(rows = vars(env_width, compet_status),
               cols = vars(cwm_name),
               labeller = label_compet_env) +
    ylim(0, NA) +
    scale_fill_viridis_d("Trait\nCorrelations",
                         labels = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7")) +
    guides(fill = guide_legend(override.aes = list(size = 4))) +
    labs(subtitle = "R2 of trait2 CWM ~ environment",
         x = "Scenario",
         y = expression("R"^2)) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "top")

@@

```{r link_r2_cwm_trait_var}
all_trait_var = all_df %>%
    filter(N > 0) %>%
    group_by(env_width, compet_status, cor_level, scenario, patch) %>%
    summarise_at(vars(matches("trait[123]$")), funs(var = var(.))) %>%
    ungroup() %>%
    mutate(patch_optim = as.numeric(gsub("patches", "", patch))) %>%
    gather("trait_name", "trait_value", contains("trait"))

ggplot(all_trait_var, aes(scenario, trait_value, fill = fct_rev(cor_level))) +
    geom_boxplot() +
    facet_grid(rows = vars(env_width, compet_status),
               cols = vars(trait_name),
               labeller = label_compet_env,
               scales = "free_y") +
        scale_fill_viridis_d("Trait\nCorrelations",
                             labels = c(no_cor   = "r = 0",
                                        low_cor  = "r = 0.3",
                                        high_cor = "r = 0.7")) +
        labs(y = "Variance of trait across all patches")
```

```{r plot_trait_var_env}
plot_trait_var_env_constant = ggplot(all_trait_var %>%
                                         filter(env_width == "constant"),
                                     aes(patch_optim, trait_value,
                                         color = trait_name,
                                         linetype = compet_status)) +
    geom_line() +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(name = "Trait",
                         labels = c(trait1_var = "Trait 1",
                                    trait2_var = "Trait 2",
                                    trait3_var = "Trait 3")) +
    scale_linetype_discrete(name = NULL,
                            labels = c(compet    = "Competition",
                                       no_compet = "Only intra comp.")) +
    labs(x = "Environment",
         y = "Trait Variance",
         subtitle = "Constant Environment") +
    theme(legend.position = "top")

@@

plot_trait_var_env_varying
```

@@

```{r cwv_envt}
var_df %>%
    select(-contains("cwm")) %>%
    filter(compet_status == "no_compet") %>%
    gather("trait_name", "trait_value", contains("trait")) %>%
    group_by(compet_status, cor_level, scenario, patch, trait_name) %>%
    summarise(trait_cwv = Weighted.Desc.Stat::w.var(trait_value, mu = N)) %>%
    mutate(patch_optim = gsub("patches", "", patch) %>%
               as.numeric()) %>%
    ggplot(aes(patch_optim, trait_cwv, color = trait_name)) +
    geom_point() +
    geom_smooth(se = FALSE) +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                                 low_cor  = "r = 0.3",
                                                 high_cor = "r = 0.7"))) +
    scale_color_discrete(labels = c(trait1_cwm = "Trait 1",
                                    trait2_cwm = "Trait 2",
                                    trait3_cwm = "Trait 3")) +
    labs(x = "Environment",
         y = "Community-Weighted Variance (CWV)",
         color = NULL,
         subtitle = paste0("Varying environment; ",
                           d * 100, "% dispersal;",
                           " Only intra comp.")) +
    theme(legend.position = "top")
